Synpotic Soil Characterization

### 2025-09-14 3-reports/manuscript_figures.Rmd
update sensor graphs

@@

@@

troll %>% 
  reorder_transect() %>% 
  ggplot(aes(x = datetime_est, y = wl_below_surface_m, color = transect))+
  geom_hline(yintercept = 0, alpha = 0.8)+
  geom_line(aes(y = rollmean), linewidth = 1)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "marsh"), 
                     values = pal_transect)+
  labs(x = "",
       y = "Water level below surface (m)",
       color = "")+
  theme_kp()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 14, angle = 45, hjust = 1))   ##

@@

```{r}
water_table %>% reorder_transect() %>% knitr::kable()
```

@@

```{r}
percent_flooded %>% reorder_transect() %>% knitr::kable()
```

>>>>

print("2022-24")

@@

print("Jan-Dec 2023")

vwc_data %>% 
  filter(value > 0) %>% 
  filter(datetime_est > "2023-01-01") %>% 
  filter(datetime_est < "2023-12-31") %>% 
  reorder_site() %>% 
  reorder_transect() %>% 
  ggplot(aes(x = datetime_est, y = value, color = transect))+
  geom_line()+
  #  facet_wrap(~ site + transect)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey")) +
  scale_color_manual(breaks = c("upland", "transition", "wte", "marsh"), 
                     values = pal_transect)+
  labs(x = "", 
       y = "Water content (% v/v)",
       color = "")+
  theme_kp()+
  theme(axis.text.x = element_text(size = 14, angle = 45, hjust = 1),
        panel.grid = element_blank())

@@

print("2022-24")

troll %>% 
  reorder_transect() %>% 
  ggplot(aes(x = datetime_est, y = wl_below_surface_m, color = transect))+
  geom_hline(yintercept = 0, alpha = 0.8)+
  geom_line(aes(y = wl_below_surface_m), linewidth = 1)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "marsh"), 
                     values = pal_transect)+
  labs(x = "",
       y = "Water level below surface (m)",
       color = "")+
  theme_kp()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 14, angle = 45, hjust = 1))

print("Jan-Dec 2023")

troll %>% 
  filter(datetime_est > "2023-01-01") %>% 
  filter(datetime_est < "2023-12-31") %>% 
  reorder_transect() %>% 
  ggplot(aes(x = datetime_est, y = wl_below_surface_m, color = transect))+
  geom_hline(yintercept = 0, alpha = 0.8)+
  geom_line(aes(y = wl_below_surface_m), linewidth = 1)+
  facet_nested_wrap(~region + site,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("upland", "transition", "wte", "marsh"), 
                     values = pal_transect)+
  labs(x = "",
       y = "Water level below surface (m)",
       color = "")+
  theme_kp()+
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(size = 14, angle = 45, hjust = 1))

@@

```{r}
print("Jan-Dec 2023")

water_table %>% reorder_transect() %>% knitr::kable()
```

@@

```{r}
print("Jan-Dec 2023")

percent_flooded %>% reorder_transect() %>% knitr::kable()
```
